---
title: "Getting And Cleaning Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('rough.R')
```

## Getting and Cleaning Data
# Variables
The variables and Columns are explained here.

## subjects
This is a factor vairable of 30 volunteers each labeled with numeric values from 1-30

## activities
This is a factor variable of 6 activities that were performed.
```{r act, echo=FALSE}
levels(act)
```
## variabletype

This is a factor variable of ids for different feature measurements pertaining to this final tidy data.
```{r f, echo=FALSE}
knitr::kable(f)
```

## description
This is a short description of the specific measured feature retrieved from features.txt data set

## The following a broken down descriptions of the above said description variable
### domain
```{r echo=FALSE}
levels(f$domain)
```
### acceleration
```{r echo=FALSE}
levels(f$acceleration)
```
### instrument
```{r echo=FALSE}
levels(f$instrument)
```
### jerk
```{r echo=FALSE}
levels(f$jerk)
```
### statistic
```{r echo=FALSE}
levels(f$statistic)
```
### axis
```{r echo=FALSE}
levels(f$axis)
```

## mean
The mean value of the groups of values for each variable, each activity and each subject

# Summary of Data
The data collected was a dataset of various measured features from sensors on a Samsung SII by 30 volunteers performing 6 activities. The volunteers where broken into two sets; training and test.
## What was done
The two sets were merged with their respective activity label and subject label. Then expanded the table to transform each measured variable and its value from the columns to rows
```{r}
data.frame(name=c("Jane","John","Peter"),age=c(23,24,17),country=c("USA","GHA","ENG"))
melt(data.frame(name=c("Jane","John","Peter"),age=c(23,24,17),country=c("USA","GHA","ENG")),id="name",measure.vars = c("age","country"))
```
To Get the table narrowed so that each row focuses on one measured variable type.
Then means were calculated from grouped sets.

Code for cleaning is found in *run_analysis.R*.
Tada! Tidy Dataset for you analysis is saved in either *tidyData.txt* / *tidyData.csv*